\bibliographystyle{IEEEtran}
%\bibliography{IEEEabrv,./7-Bibliografia/Biblio}

\begin{thebibliography}{9} 

\bibitem{tor} R. Dingledine, N. Mathewson, and P. Syverson,\textit{"TOR: The second-generation onion router,"} In USENIX Security Symposium (San Diego, CA, 2004), USENIX Association, pp. 303-320.

\bibitem{tormetrics} Tor Metrics \url{https://metrics.torproject.org/}, [Accesso: 13 Settembre 2016].

\bibitem{torspec} Tor's protocol specifications \url{https://gitweb.torproject.org/torspec.git/tree/dir-spec.txt}, [Accesso: 13 Settembre 2016].

\bibitem{torbridge} Z. Ling, J. Luo, W. Yu, M. Yang, and X. Fu,\textit{"Extensive analysis and large-scale empirical evaluation of Tor bridge discovery,"} in Proc. IEEE INFOCOM, 2012, pp. 2381-2389.

\bibitem{gfc} P. Winter, S. Lindskog, \textit{"How the Great Firewall of China is Blocking Tor,"} Free and Open Communications on the Internet, 2012.

\bibitem{meek} The Tor Project. Meek \url{https://trac.torproject.org/projects/tor/wiki/doc/meek}, [Accesso: 13 Settembre 2016].

\bibitem{domainfronting} D. Fifield, C. Lan, R. Hynes, P. Wegmann, and V. Paxson, \textit{"Blocking-resistant communication through domain fronting,"} Proceedings on Privacy Enhancing Technologies 2015, pp. 1-19.

\bibitem{cellflood} M. V. Barbera, V. P. Kemerlis, V. Pappas, and A. Keromytis, \textit{"CellFlood: Attacking Tor Onion Routers on the Cheap,"} in Proc. ESORICS, Sep. 2013, pp. 664-681.

\bibitem{sniper} R. Jansen, F. Tschorsch, A. Johnson, and B. Scheuermann, \textit{"The sniper attack: Anonymously deanonymizing and disabling the Tor network,"} in Proc. 21st Annu, Symp. NDSS, Feb. 2014, pp. 1-15.

\bibitem{packetspinning} V. Pappas, E. Athanasopoulos, S. Ioannidis, and E. P. Markatos,\textit{"Compromising Anonymity Using Packet Spinning,"} in ISC 08, Sep. 2008.

\bibitem{lochidd} Lasse {\O}verlier and Paul Syverson, \textit{"Locating Hidden Servers,"} in Proceedings of the IEEE Security and Privacy Symposium (S\&P), May 2006.

\bibitem{survey} E. Erdin, C. Zachor, and M. H. Gunes, \textit{"How to Find Hidden Users: A Survey of Attacks on Anonymity Networks,"}. IEEE Commun. Surv. Tutorials, vol. 17, no. 4, pp. 2296-2316, 2015.

\end{thebibliography}